Model of lens candidates from Space Warps CFHTLS

### 2016-05-12 paper2.tex
removing subcaption
added table
tick/cross ding
working on text

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
\usepackage{silence} % silence error warinings
\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
\hbadness = 5000
\vbadness = 10000
\usepackage{}

@@

% Only include extra packages if you really need them. Common packages are:
%\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{graphicx} % Including figure files
\usepackage[skip=0pt]{subcaption}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?

% TODO stuff, comment out for final submit
\usepackage{todonotes} % as long as we are editing...
\usepackage{showframe} % for debug
\overfullrule=5pt      % show overfull boxes

@@

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

\newcommand{\inclfig}[2]{
  \centering
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_input}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img1}
  \end{subfigure}%
  \\[-1px]%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img3_ipol}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img2}
  \end{subfigure}%
  \\[-1px]%
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
  \end{subfigure}
}

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{Preliminary categorisation of SpaceWarps candidates}

@@

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Here we cite \cite{2015MNRAS.447.2170K}.

@@

@@

The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2340K}.
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\section{Results}
Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
The data available is shown in \figref{SW58}.
\todo{better explain criterias?}
The following sections list all the models for all the categories, each with a short explanation of the reasons.
Additionally, selected models are presented in figures for demonstration.

% 
% \subsection{Spectra}
% Candidates to follow up with a spectral analysis. 
% 
% 
% \subsection{Bad models}
% Candidates that need more work to be modelled.
% Or that have features that are hard / impossible to model with the current SpaghettiLens version.
% Examples are group lenses
% 
% 
% 
% \subsection{Non Lenses}
% Those are most probly non lenses,

@@

\lenstitle{SW58 (ASW0007iwp)} 
  nice arc, no counter image;
  model prediction really good;
  masses ok

good example of plausible

% \begin{figure}
% 	\inclfig{SW45}{ASW000024id_TSKKYHD3CB}
% \end{figure}

@@

(like 4dv8 collective modelling)

@@

@@

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli.bib} % if your bibtex file is called example.bib

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[fleqn,usenatbib]{mnras}

%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
\usepackage{silence} % silence error warinings
\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
\hbadness = 5000
\vbadness = 10000
% \usepackage{}

@@

% Only include extra packages if you really need them. Common packages are:
%\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{graphicx} % Including figure files
%\usepackage[skip=0pt]{subcaption}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{pifont}	% Extra maths symbols
%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?

% TODO stuff, comment out for final submit
\usepackage{todonotes} % as long as we are editing...
%\usepackage{showframe} % for debug
%\overfullrule=5pt      % show overfull boxes

@@

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_input}%
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img1}
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img3_ipol}%
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img2}
	\includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand*{\rot}{\rotatebox{90}}
\newcommand*{\OK}{\ding{51}}
\newcommand*{\NO}{\ding{55}}

@@

\title[Short title, max. 45 characters]{Model of lens candidates from
  Space Warps CFHTLS}

@@

% These dates will be filled out by the publisher
% \date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

@@

@@

Space Warps \citep{2016MNRAS.455.1171M} found lens candidates
\citep{2016MNRAS.455.1191M}.

Modelling method \citep{2015MNRAS.447.2170K}.

@@

\subsection{Stellar mass}

@@

The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\section{Example systems}

Plausible

Uncertain

\section{Summary of models}

Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
The data available is shown in \figref{SW58}.
\todo{better explain criterias?}
The following sections list all the models for all the categories, each with a short explanation of the reasons.
Additionally, selected models are presented in figures for demonstration.

@@

\lenstitle{SW58 (ASW0007iwp)} 
  nice arc, no counter image;
  model prediction really good;
  masses ok
  good example of plausible

@@

\lenstitle{SW36 (ASW000096t)}
(like 4dv8 collective modelling)

@@

\subsection{Table}

\begin{table*}
  \caption{Categorisation of SW models}
  \label{tab:models}
\include{table}
\end{table*}

\section{Discussions}

@@

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli} % if your bibtex file is called example.bib

@@
